---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# docsifier

[WORK IN PROGRESS - USE WITH CAUTION]

<!-- badges: start -->
<!-- badges: end -->
  
* [Installation](#installation)
* [Purpose of `docsifier`](#purpose)
* [How to use](#howto)
* [Experimental](#experimental)
* [Code of Conduct](#CoC)
  
  
The goal of docsifier is to generate the structure to use [docsify.js](https://docsify.js.org/#/) for the documentation of an R package.

## Installation

You can install the development version with: 

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("etiennebacher/docsifier")
```

## Purpose of `docsifier`

Docsify uses two things:

* an index written in HTML that contains several options for the page, such as the presence of a navbar, a coverpage, the color of the background, etc.

* one or several Markdown files that populate the page. These files contain the documentation that you want to include in your page.

`docsifier` can't create the documentation for you, this is still your work. However, it provides helpers so that the creation of the documentation with Docsify is easier.


## How to use

**Note that `docsifier` only works for R packages.** `docsifier` provides three functions: `use_docsifier()`, `add_rmd()` and `add_md()`.

The first one creates the bare structure that Docsify needs: a folder "docs" (if there isn't already one), an HTML file called `index.html`, and a Markdown file called `homepage.md`.

For example, this is the folder structure of this package (at its early stage) before `use_docsifier()`...

```{r echo = FALSE}
fs::dir_tree(type = "directory")
```

... and after its use:

```{r echo = FALSE, message = FALSE}
devtools::load_all()
```
```{r echo = TRUE}
use_docsify(open = FALSE)
```
```{r echo = FALSE}
fs::dir_tree(type = "directory")
```
```{r echo = FALSE}
fs::dir_tree("docs")
```


The two other functions are `add_rmd()` `add_md()`. These functions are very simple: they just create respectively an `.Rmd` and an `.md` file in "docs" to save some time.


## Experimental

A set of functions to install and run docsify:

* `dep_available()` to check if Node.js and npm are installed (should work)

* `install_docsify()` to install docsify on user's computer (doesn't work at all)

* `preview_docsify()` to preview the documentation in a webpage (works but can't be stopped)


## Code of Conduct

Please note that the docsifier project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.




